### 2023-06-09 proofs/tex/alg-pos-subtyping-lemmas.tex
Add algorithmic typing

    \item \label{case:pos-subt-soundness:shift} 
     \ruleref{\ottdruleAShiftDLabel} then
    $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ us]]$ has shape $[[Γ;Θ ⊨ ↓uN ≥ ↓iM ⫤ us]]$.\\
    Then the next step of the algorithm is the unification of $[[nf(uN)]]$ and $[[nf(iM)]]$.
    By the soundness of the unification algorithm (\cref{lemma:unification-soundness}),
    it returns an equivalence-only solution $[[us]]$ such that $[[us : Ord uv uN]]$.
    By \cref{todo}, since $[[us]]$ is equivalence-only and $[[Γ ⊢ Θ]]$, $[[Θ ⊢ us' ⇒ us]]$ means 
    $[[ Γ ⊢ Sub us' ≈ Sub us : Ord uv uN ]]$ as substitutions.
    $[[ [us]nf(uN) = nf(iM) ]]$ implies $[[Γ ⊢ [us]nf(uN) ≈ nf(iM)]]$, and then 
        $[[Γ ⊢ [us']nf(uN) ≈ nf(iM)]]$. \ilyam{add lemmas}

>>>>

    \item \label{case:pos-subt-soundness:shift} 
     \ruleref{\ottdruleAShiftDLabel} then
    $[[Γ ; Θ ⊨ uP ≥ iQ ⫤ us]]$ has shape $[[Γ;Θ ⊨ ↓uN ≥ ↓iM ⫤ us]]$.\\
    Then the next step of the algorithm is the unification of $[[nf(uN)]]$ and $[[nf(iM)]]$.
    By the soundness of the unification algorithm (\cref{lemma:unification-soundness}),
    it returns an equivalence-only solution $[[us]]$ such that $[[us : Θ | uv uN]]$.
    By \cref{todo}, since $[[us]]$ is equivalence-only and $[[Γ ⊢ Θ]]$, $[[Θ ⊢ us' ⇒ us]]$ means 
    $[[ Γ ⊢ Sub us' ≈ Sub us : Ord uv uN ]]$ as substitutions.
    $[[ [us]nf(uN) = nf(iM) ]]$ implies $[[Γ ⊢ [us]nf(uN) ≈ nf(iM)]]$, and then 
        $[[Γ ⊢ [us']nf(uN) ≈ nf(iM)]]$. \ilyam{add lemmas}
